### 2015-07-14 ids-fusion.tex

>>>>

% New paragraph to address
% [[file:todo.txt::*Review%201:%20learned%20or%20hand-made%20domains?][Review 1: learned or hand-made domains?]]
% and [[file:todo.txt::*Review%201:%20Hand-made%20vs.%20generated][Review 1: Hand-made vs. generated]]
Some of our reviewers expressed the concern that we would have difficulty
\emph{modeling} the rare events in \ids fusion.  This problem does not, in fact,
arise, for three reasons.  One is that these attack events are not rare in the
world: they are rare with respect to our sampling rate.  As we point out above,
if we are sampling individual packets, the probability of any attack is
vanishingly small, but that doesn't mean that attacks are rare at the
``macroscopic'' level.  Second, our causal models are limited to models of
sensing and fusion, part/whole, and class/subclass relations.  These models are
very simply generated by rules.  Finally, the \ids developers provide us initial
ontologies of events implicitly with their rules.  Our knowledge engineering
aims at smoothing inconsistencies between these implicit ontologies, and
extending causal models by identifying cases where \ids developers have
provided incorrect intuitions about the events their systems detect.
At any rate, this concern is not relevant to the evaluation of the uncertainty
calculus, which is our focus in this paper.
